Study of the hadronization of charged pions

### 2016-10-11 AnalysisNote.tex
Corrections from Lamiaa

The goals of the experiment E-02-104 are to study both quark propagation
and hadronization dynamic using various nuclear target.
In this analysis we focus on two particles, the positive and negative pions
to constrain theoritical models using precise multidimensional analysis.

>>>>

The goals of the experiment E-02-104 are to study both quark propagation
and hadronization dynamics using various nuclear target.
In this analysis we focus on two particles, the positive and negative pions
to constrain theoritical models using a precise multidimensional analysis.

### 2016-10-11 chap5.tex
Small fix
Corrections from Lamiaa

This chapter treats of the analysis of the data taken in CLAS for the 
experiments E-02-104 \cite{Brooks:2002aa} and E-02-110 \cite{Hafidi:2002aa}.
The code name for the run is {\it eg2}, it was composed of three phases 
labeled {\it a}, {\it b} and {\it c}. The analysis is performed on the data 
collected in the beginning of 2004 during the third phase ({\it eg2c}), for 
which the beam energy was 5.014~GeV\footnote{The other phases of the run gave only small 
amounts of data at a beam energy of 4~GeV that we decided not to use for this analysis.}.

As the two experiments, running simultaneously, aimed at comparing deuterium 
with heavier nuclei, it was decided to use a double target system 
\cite{Hakobyan:2008zz}. The first target is filled with liquid deuterium and 
the second is a solid target. The latter can be made of carbon, aluminum, 
iron, tin or lead and changed remotely (the system is shown in figure 
\ref{fig:phototarget}). The two targets are separated by only 4~cm in order to reduce
the acceptance differences between them. The 
advantage to have the two targets in the beam line simultaneously
is that several systematic effects related to the beam 
and detector properties will cancel in the nuclear ratio.

\begin{figure}[htbp]
\centering
\includegraphics[width=7cm] {chap5-fig/PhTar.jpg} 
\caption {Picture of the target system of the {\it eg2} run. The cryogenic target is 
in the back, enveloped in aluminum foils. The solid targets are held by mechanical arms
allowing to change targets remotely, in the picture the top arm is in the beam line.}
\label{fig:phototarget}
\end{figure}

@@

Once particles are identified, we can extract the observables (multiplicity 
ratio and transverse momentum broadening). The method is presented in the 
section \ref{sec:obs}, however these need several corrections presented in the 
section \ref{sec:corrections}. The 
two main corrections are the acceptance of the detector and the radiative 
effects, both are evaluated using Monte-Carlo generator. The evaluation of 
the systematic errors is presented in the section \ref{sec:TotSys}.
The analysis' final results are presented and discussed in the next chapter.

@@

\begin{table}[tbp]
  \centering
  \begin{tabular}{@{} cc @{}}
    \hline
    Momentum bin (GeV/c)& Parameter b \\ 
    \hline
    0.5 - 0.7 & 0.85 \\
    0.7 - 0.9 & 0.8  \\
    0.9 - 1.1 & 0.85 \\
    1.1 - 1.3 & 1.05 \\
    1.3 - 1.5 & 1.1  \\
    1.5 - 1.7 & 1.35 \\
    1.7 - 1.9 & 1.35 \\
    1.9 - 2.1 & 1.45 \\
    2.1 - 2.3 & 1.35 \\
    2.3 - 2.5 & 1.35 \\
    2.5 - 2.7 & 1.35 \\
    2.7 - 2.9 & 1.3  \\
    2.9 - 3.1 & 1.35 \\
    3.1 - 3.3 & 1.35 \\
    3.3 - 3.5 & 1.5  \\
    3.5 - 3.7 & 1.6  \\
    3.7 - 3.9 & 1.8  \\
    3.9 - 4.1 & 1.8  \\
    4.1 - 4.3 & 1.8  \\
    4.3 - 4.5 & 1.8  \\
    \hline
  \end{tabular}
  \caption{Values of the parameter $b$ used in equation \ref{einout} for 
           different momentum ranges.}
  \label{tab:ecoutin-par}
\end{table}

\begin{figure}[p]
\centering
\includegraphics[width=14cm] {chap5-fig/fig02.jpg} 
\caption {Energy deposited in the inner part of the EC ($E_{in})$) as a function of the 
energy deposited in the outer part ($E_{out})$), both divided by the momentum of the 
particle. Each panel is for a different momentum range, the red lines 
illustrate the cuts from equation \ref{einout}.}
\label{eleEC}
\end{figure}

@@

In the CC, the mean number of photo-electrons\footnote{Photo-electrons are 
electrons produced in the front window of the Photo-Multiplier Tube (PMT) by 
single photons.} from a high energy electron is expected to be around 10.
However, hadrons can generate noise due to $\delta$ electrons produced in 
the materials of the detector. This signal is expected around 
one photo-electron, to remove it, we keep only tracks with more than 
2.5~photo-electrons (figure \ref{delta}).

@@

To select electrons, we also require that the particles are negatively charged, 
according to the bending direction of the tracks in the drift chamber.
Positively charged particles are identified as positrons. In the rest of the 
analysis we use events with only one electron and no positron to avoid any 
confusion between the scattered electron and electrons from hadronic decays or 
photon conversion.

@@

The identification consists mostly of a time of flight (TOF) test. We define 
$\Delta \beta = \beta_{measured} - {p \over \sqrt{p^2 + m_\pi^2}}$ and request 
$\Delta \beta$ to be zero within $\pm 0.03$. Figure \ref{PionTOF} illustrates 
the effect of this cut. We notice that there is not much negative kaons or 
anti-protons. Therefore, the contamination from these should be small (see 
section \ref{SysId} for more detailed analysis).

@@

In principle, pion identification could be improved using the Cherenkov counter 
for momentum higher than 2.5~GeV/c. But, the low efficiency observed (figure 
\ref{PionCC}), especially at momentum close to the threshold ($\sim$25\% at 
2.5~GeV/c and $\sim$50\% at 3~GeV/c), makes its use less compelling. 
Moreover, as only a very small amount of $K^-$ and no $\bar p$ are present on 
the figure \ref{PionTOF}, we decided not to use the CC for pion identification.

@@

The identification of positively charged pions is similar to that of negative 
pions. However, the time of flight plot is significantly more busy (figure 
\ref{PipTOF}), showing significant contamination from $K^+$ and protons at 
high momentum. As the CC is not efficient enough for hadron separation, the 
numerous kaons and protons should be removed by a tighter TOF cut:

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=8cm] {chap5-fig/pip_data.png} 
\caption {$\Delta \beta$ as a 
function of momentum (GeV/c). Only positive particles are shown, the red 
lines are the cuts applied to select positive pions. The blue lines indicate 
theoretical positions for other particle masses, are plotted from top to 
bottom the lines for positrons, muons, kaons and protons.}
\label{PipTOF}
\end{figure}

@@

The detected electrons are associated with the solid target if their vertex 
position is at less than 1.5~cm ($\sim$3~$\sigma$) from the value of table 
\ref{tab:targets}. For the liquid target, the cut is larger, 2 cm, in order to 
account for the size of the target (see figure \ref{vertex}). The vertex of 
the pions is checked against the electron one and we request that 
$| Vz^{e^-} - Vz^{\pi} | < 3$ cm (see figure \ref{fig:dvzpi}).

@@

To check the quality of the runs\footnote{Runs correspond roughly to two hours
of data, they can be smaller in case of problem.}, we look at the ratio of the number of 
scattered electrons, between the liquid and solid targets. If the beam is 
hitting other materials than the targets or if the detector is not working 
properly this ratio can be off and indicates a problematic run. The figure 
\ref{DataQ} shows the values obtained; we fit the 
mean value for all runs of each target and eliminate runs away by more than 
5$\sigma$. We note that the ratios are coherent with target thicknesses given 
in \cite{Hakobyan:2008zz} except for carbon. Because of this, the density of 
the carbon target was remeasured recently and found to be coherent with the 
data\footnote{i.e. (1.747+/-0.0007)g/cm$^3$ instead of 2.235 g/cm$^3$}.

@@

Since we are interested in deep inelastic scattering, we use the following 
cuts: $Q^2 > 1$~GeV$^2$/c$^2$ and $W > 2$~GeV. We also apply a cut $y < 0.85$ 
which corresponds to low energy electrons. These are removed beacause they are
significantly affected by radiative effects and at the limit of our trigger 
threshold.

@@

However, the implementation of acceptance and radiative corrections is done through weights
given to each events depending on their kinematics. The multiplicity ratio then becomes
\begin{equation}
R_A^h (Q^2,\nu,z_h,P_\perp^2) = {{\sum \omega_A^h (Q^2,\nu,z_h,P_\perp^2) / \sum \omega_A^e (Q^2,\nu)} 
                       \over {\sum \omega_D^h (Q^2,\nu,z_h,P_\perp^2) / \sum \omega_D^e (Q^2,\nu)}},
\end{equation}
with $\omega$ the weights and all the sums running over all measured particles.
The expression for the transverse momentum broadening remains
\begin{equation}
\Delta \langle P_\perp^2 \rangle = \langle P_\perp^2 \rangle_A - \langle P_\perp^2 \rangle_D,
\end{equation}
but with
\begin{equation}
\langle P_\perp^2 \rangle = {\sum \left ( P_\perp^2 \times \omega (Q^2,\nu,z_h,P_\perp^2) \right ) \over \sum \omega (Q^2,\nu,z_h,P_\perp^2)}.
\end{equation}

This expressions leads to new expressions for the statistical error uncertainties taking weights into account: 
\begin{equation}
{\delta \left ( R_A^h \right ) \over R_A^h} = 
      \sqrt{ \left ( {\sum {\omega^h_A}^2 \over \left (\sum \omega^h_A \right )^2} \right ) 
           + \left ( {\sum {\omega^e_A}^2 \over \left (\sum \omega^e_A \right )^2} \right ) 
           + \left ( {\sum {\omega^h_D}^2 \over \left (\sum \omega^h_D \right )^2} \right ) 
           + \left ( {\sum {\omega^e_D}^2 \over \left (\sum \omega^e_D \right )^2} \right ) }
\end{equation}
 and 
\begin{equation}
\begin{split}
\left ( \delta \left ( \Delta \langle P_\perp^2 \rangle \right ) \right )^2 = 
   \left ({{\sum \omega^h_A P_\perp^4 }\over{\sum \omega^h_A}} - \left ({\sum \omega^h_A P_\perp^2 }\over{\sum \omega^h_A}\right )^2 \right ) 
         \times \left ( {\sum \left ( {\omega^h_A}^2 \right ) \over \left ( \sum \omega^h_A \right ) ^2 }\right ) \\
 + \left ({{\sum \omega^h_D P_\perp^4 }\over{\sum \omega^h_D}} - \left ({\sum \omega^h_D P_\perp^2 }\over{\sum \omega^h_D}\right )^2 \right ) 
	 \times \left ( {\sum \left ( {\omega^h_D}^2 \right ) \over \left ( \sum \omega^h_D \right ) ^2 }\right ).
\end{split}
\end{equation}

@@

We present in figure \ref{fig:prelim} few preliminary results, before the application 
of any correction, to 
provide a first idea on data quality. These preliminary results will also be used to 
illustrate the effects of the corrections discussed below.

@@

The acceptance correction consists of applying weights to the events in 
experimental data to correct for the inefficient parts of the detectors.
Incidentally, it also corrects for small other issues of detection,
such as misidentification and scattering on detectors materials. The quality 
of the correction depends on the ability of the simulation to reproduce the 
experiment, the statistics accumulated and the size of interfering effects, such 
as bin migration.

@@

Then the simulated data are processed in a similar way than the experimental data by 
applying the cuts described in the section \ref{sec:pid}. Overall the 
simulation reproduces quite well the detectors responses, yet two issues might 
affect us and have to be understood. First, the efficiency of the CC is 
overestimated in the simulation. 
On the electron side the signal is a little stronger in the simulation (11 
photo-electrons) compared to experimental data (8 photo-electrons), but this 
feature should not affect us too much, because we are cutting only the tail of the 
distribution in both cases. 
%For pion identification, as mentioned in section \ref{PiId},
%we do not use the CC because of its low efficiency.
%We observe, in the simulation, a much better detector response than in experiment 
%(figure \ref{simPionCC} compared to figure \ref{PionCC}), this result also 
%advocates against the use of the CC in the 
%particle identification. Indeed, the poor reproduction of the experimental 
%signal would introduce a bias in our acceptance correction. 
Second, in figure \ref{vertex} the cuts on vertex are shifted from one sector 
to another, since the simulation have perfect alignment of beam with CLAS this 
feature is not present in the simulated data. Therefore, we do not apply the 
shift from the table \ref{tab:vertex} to the simulation; results are shown in 
figure~\ref{simvertex}.

%\begin{figure}[tpb]
%\centering
%\includegraphics[width=9cm] {chap5-fig/fig06simul.png} 
%\caption {Histograms of momentum (GeV/c) of $\pi^-$ for {\bf simulated data}.
%In black are all identified $\pi^-$, in red pions that also fire in the 
%Cherenkov counter and in blue those that fire in the Cherenkov counter with 
%more than one photo-electron.}
%\label{simPionCC}
%\end{figure}

@@

The kinematic distributions from the simulation are compared to the 
experimental ones. This is important for the acceptance correction, to see 
whether or not, we can integrate over these variables for the correction.
Comparisons between simulation and experiment are shown in figures 
\ref{fig:compNuQ2} to \ref{fig:compPhih}. The agreement is reasonable, but not 
perfect. The differences are due to the PYTHIA simulation, which is not including some 
physical effects, such as radiative and diffractive processes.

@@

The data is corrected using weights defined as $\omega = 1/\text{Acc}$. The 
$\omega$ coefficient are calculated in many bins, in order to be independent of 
the imperfections of the event generator. However, an excess of bin could results into a strong 
bin migration\footnote{Fraction of events not reconstructed in the bin they 
were produced in.}, which might introduce a bias if it becomes a large effect.

We use a 4-dimensional binning to divide the large phase space available to 
the two particles in the measured final state. To evaluate the systematic error 
associated to the correction, we use two different binning, which are 
presented in the table \ref{tab:AcceptBinning}. The total number of bins is 
constrained by the amount of data generated and has to be maintained 
reasonably low in order to keep a good statistical precision and reasonable 
bin migration.

@@

The weights ($\omega_{\pi^\pm}(\nu,x_{Bj},p_h,t)$) are then extracted from 
the simulation using equation \ref{eq:acc}, however, it appears that these should not be used directly.
Three factors are sources of problematic bins:
\begin{itemize}
 \item too large weight values, i.e. very small acceptance;
 \item very few events reconstructed, leading to large statistical errors;
 \item large fraction of events originaly generated in another bin (bin migration).
\end{itemize}
To remove these bins we apply the following cuts:
\begin{equation} \label{eq:AccL1}
\left ({\delta \omega \over \omega}\right ) ^2 \times R_c \times \omega < 2,
\end{equation}
and
\begin{equation} \label{eq:AccL2}
N_{rec} > 4,
\end{equation}
with $\delta \omega / \omega$ the relative error on the weight and $R_c$ the 
proportion of events in the bin initially generated in another bin. Figure 
\ref{fig:AccCoef} shows the distributions of $\omega$, after the cuts. Around 
900 bins remain for both targets, but we notice that weights are much larger 
for $\pi^-$, indicating a larger correction, compared to $\pi^+$. In order to 
maximize the acceptance and reduce the sensitivity to the cuts applied on the 
weights, which are arbitrary, the bin weights are corrected. We apply a 
reweighting by calculating a new acceptance in a two dimensional binning:
\begin{equation}
\text{Acc}_2(\nu,p_h) = {\sum_{rec} \omega (\nu,x_{Bj},p_h,t)\over N_{gen}(\nu,p_h)}.
\end{equation}
with $\omega$ the previously calculated weights or one for the 
bins excluded by the cuts.
One of the criteria for setting the limits in equation \ref{eq:AccL1} and 
\ref{eq:AccL2}is to keep the reweighting factors $\omega_2 = 1/\text{Acc}_2$ at a few 
percents level.

@@

The electron acceptance, necessary in order to correct the number of electrons 
in the multiplicity ratios, is done with the same method than in the 
semi-inclusive case, but only using the two first dimensions ($\nu$ 
and $Q^2$). It is also interesting to note that no reweighting is necessary 
for electrons as all non-empty bins pass the cuts \ref{eq:AccL1} and 
\ref{eq:AccL2}.

\begin{figure}[tbp]
\centering
\includegraphics[width=7.4cm] {chap5-fig/b_RvA.png} 
\includegraphics[width=7.4cm] {chap5-fig/b_RvZ.png} 
\includegraphics[width=7.4cm] {chap5-fig/b_PvA.png} 
\includegraphics[width=7.4cm] {chap5-fig/b_PvQ2.png} 
\caption {Preliminary results are compared with results corrected for 
acceptance, for multiplicity ratios (top) and transverse momentum broadening 
(bottom). Only statistical errors are shown.}
\label{fig:AcceptPlots}
\end{figure}

Figure \ref{fig:AcceptPlots}, where only statistical errors are 
represented, shows the new results after applying the acceptance correction.
The acceptance effects appear to be of $\sim 10$\% for multiplicity ratios and 
$\sim 30$\% for transverse momentum broadening. This is a surprisingly 
significant correction for the few centimeters between the two targets. The 
$\pi^-$s appears to be more affected. This is due to the inbending magnetic 
field. Indeed, the low \pt $\pi^-$s have very low acceptance, leading to large 
correction factors. The large spread in weights makes the errors 
on \dpt very large and the related results difficult to exploit. 
On the bright side, after the correction, the transverse momentum
broadening of both pions now match.

>>>>

This chapter treats the analysis of CLAS data taken for both 
experiments E-02-104 \cite{Brooks:2002aa} and E-02-110 \cite{Hafidi:2002aa}.
The run period, named {\it eg2}, was composed of three phases 
labeled {\it a}, {\it b} and {\it c}. The analysis is performed on the data 
collected in the beginning of 2004 during the third phase ({\it eg2c}), for 
which the beam energy was 5.014~GeV\footnote{The other phases of the run gave only small 
amounts of data at beam energies of 4 and 4.7~GeV, Thus, we decided not to use them 
for this analysis.}.

As the two experiments, running simultaneously, aimed at comparing deuterium 
with heavier nuclei, it was decided to use a double target system 
\cite{Hakobyan:2008zz}. The first target was filled with liquid deuterium and 
the second was a solid target. The latter was made of either carbon, aluminum, 
iron, tin or lead and was changed remotely (the system is shown in figure 
\ref{fig:phototarget}). The two targets were separated by only 4~cm in order to reduce
the acceptance differences between them. The 
advantage of having two targets simulataneously in the beam line
is that several systematic effects related to the beam 
and detector properties will cancel in the nuclear ratio.

\begin{figure}[htbp]
\centering
\includegraphics[width=7cm] {chap5-fig/PhTar.jpg} 
\caption {Picture of the target system of the {\it eg2} run. The cryogenic target is 
in the back, wrapped with aluminum foils. The solid targets are held by mechanical arms
that were remotely controled. In the picture, the top solid target is in the beam line.}
\label{fig:phototarget}
\end{figure}

@@

Once particles are identified, we can extract the observables (multiplicity 
ratios and transverse momentum broadening). The method is presented in the 
section \ref{sec:obs}, the corrections to these observables are presented in the 
section \ref{sec:corrections}. The evaluation of 
the systematic errors is presented in the section \ref{sec:TotSys}.
Finally, the analysis' final results are presented and discussed in the next chapter.

@@

\begin{table}[tbp]
  \centering
  \begin{tabular}{@{} cc @{}}
    \hline
    Momentum bin (GeV/c)& Parameter b \\ 
    \hline
    0.5 - 0.7 & 0.85 \\
    0.7 - 0.9 & 0.8  \\
    0.9 - 1.1 & 0.85 \\
    1.1 - 1.3 & 1.05 \\
    1.3 - 1.5 & 1.1  \\
    1.5 - 1.7 & 1.35 \\
    1.7 - 1.9 & 1.35 \\
    1.9 - 2.1 & 1.45 \\
    2.1 - 2.3 & 1.35 \\
    2.3 - 2.5 & 1.35 \\
    2.5 - 2.7 & 1.35 \\
    2.7 - 2.9 & 1.3  \\
    2.9 - 3.1 & 1.35 \\
    3.1 - 3.3 & 1.35 \\
    3.3 - 3.5 & 1.5  \\
    3.5 - 3.7 & 1.6  \\
    3.7 - 3.9 & 1.8  \\
    3.9 - 4.1 & 1.8  \\
    4.1 - 4.3 & 1.8  \\
    4.3 - 4.5 & 1.8  \\
    \hline
  \end{tabular}
  \caption{Values of the parameter $b$ used in equation \ref{einout} for 
           different momentum ranges~\cite{ElFassi:2008}.}
  \label{tab:ecoutin-par}
\end{table}

\begin{figure}[p]
\centering
\includegraphics[width=14cm] {chap5-fig/fig02.jpg} 
\caption {Energy deposited in the inner part of the EC ($E_{in}$) as a function of the 
energy deposited in the outer part ($E_{out}$), both divided by the momentum of the 
particle. Each panel is for a different momentum range, the red lines 
illustrate the cuts from equation \ref{einout}.}
\label{eleEC}
\end{figure}

@@

In the CC, the mean number of photo-electrons\footnote{Photo-electrons are 
electrons produced in the front window of the Photo-Multiplier Tube (PMT) by 
single photons.} from a high energy electron is expected to be around 10.
However, hadrons can generate noise due to $\delta$ electrons produced in 
the materials of the detector. This signal is expected to be around 
one to two photo-electrons, hence to remove it we keep only tracks with more than 
2.5~photo-electrons (figure \ref{delta}).

@@

To select electrons, we also require that the particles are negatively charged, 
which is determined based on the bending direction of the track in the drift chamber.
Positively charged particles verifying electrons' cuts are identified as 
positrons. In the rest of the 
analysis we use only events with a single electron and no positron to avoid any 
confusion between the scattered electron and electrons originating from hadronic decays or 
a photon conversion.

@@

The identification consists mostly of a time of flight (TOF) test. We define 
the relativistic particles' velocity difference as
$\Delta \beta = \beta_{measured} - {p \over \sqrt{p^2 + m_\pi^2}}$ and request 
$\Delta \beta$ to be zero within $\pm 0.03$. Figure \ref{PionTOF} illustrates 
the effect of this cut. We notice that there is not much negative kaons or 
anti-protons. Therefore, the contamination from these should be small (see 
section \ref{SysId} for more detailed analysis).

@@

In principle, pion identification could be improved using the Cherenkov counter 
for momentum higher than 2.5~GeV/c. But, the low efficiency observed (figure 
\ref{PionCC}), especially at momentum close to the threshold ($\sim$25\% at 
2.5~GeV/c and $\sim$50\% at 3~GeV/c), makes its use less compelling. 
Moreover, as only a very small amount of $K^-$ and no $\bar p$ are present on 
the figure \ref{PionTOF}, we decided to not use the CC for the pion identification.

@@

The identification of positively charged pions is similar to that of negative 
pions. However, the time of flight plot is significantly more busy (figure 
\ref{PipTOF}), showing a significant contamination from $K^+$ and protons at 
high momentum. As the CC is not efficient enough for hadron separation, the 
numerous kaons and protons should be removed by a tighter TOF cut:

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=8cm] {chap5-fig/pip_data.png} 
\caption {$\Delta \beta$ as a 
function of momentum (GeV/c). Only positive particles are shown, the red 
lines are the cuts applied to select positive pions. The blue lines indicate 
the theoretical positions for other particles, we plotted from top to 
bottom the lines for positrons, muons, kaons and protons.}
\label{PipTOF}
\end{figure}

@@

The detected electrons are associated with the solid target if their vertex 
position is less than 1.5~cm ($\sim$3~$\sigma$) from the value of table 
\ref{tab:targets}. For the liquid target, the cut is larger, 2 cm, in order to 
account for the size of the target (see figure \ref{vertex}). The vertex of 
the pions is checked against the electron one and we request that 
$| Vz^{e^-} - Vz^{\pi} | < 3$ cm (see figure \ref{fig:dvzpi}).

@@

To check the quality of the runs\footnote{Runs correspond roughly to two hours
of data, they can be smaller in case of problems.}, we looked at the ratio of the number of 
scattered electrons, between the liquid and solid targets. If the beam is 
hitting other materials than the targets or if the detector is not working 
properly this ratio can be off and indicates a problematic run. The figure 
\ref{DataQ} shows the values obtained; we fit the 
mean value for all runs of each target and eliminate runs away by more than 
5$\sigma$. We note that the ratios are coherent with target thicknesses given 
in \cite{Hakobyan:2008zz} except for carbon. Because of this, the density of 
the carbon target was remeasured recently and found to be coherent with the 
data\footnote{i.e. (1.747+/-0.0007)g/cm$^3$ instead of 2.235 g/cm$^3$}.

@@

Since we are interested in deep inelastic scattering, we use the following 
cuts: $Q^2 > 1$~GeV$^2$/c$^2$ and $W > 2$~GeV. We also apply a cut on the 
fraction of energy transferred $y = \nu/E_{beam} < 0.85$.
This corresponds to removing the low energy electrons because they are
significantly affected by radiative effects and sat the limit of our trigger 
threshold.

@@

However, the implementation of acceptance and radiative corrections is done through weights
given to each events depending on their kinematics. The multiplicity ratio then becomes
\begin{equation}
R_A^h (Q^2,\nu,z_h,P_\perp^2) = {{\sum \omega_A^h (Q^2,\nu,z_h,P_\perp^2) / \sum \omega_A^e (Q^2,\nu)} 
                       \over {\sum \omega_D^h (Q^2,\nu,z_h,P_\perp^2) / \sum \omega_D^e (Q^2,\nu)}},
\end{equation}
with $\omega$ the weight associated with the event and the sums running over all measured 
particles. The expression for the transverse momentum broadening remains
\begin{equation}
\Delta \langle P_\perp^2 \rangle = \langle P_\perp^2 \rangle_A - \langle P_\perp^2 \rangle_D,
\end{equation}
but with
\begin{equation}
\langle P_\perp^2 \rangle = {\sum \left ( P_\perp^2 \times \omega (Q^2,\nu,z_h,P_\perp^2) \right ) \over \sum \omega (Q^2,\nu,z_h,P_\perp^2)}.
\end{equation}

Thus, new expressions are also needed for the statistical error uncertainties: 
\begin{equation}
{\delta \left ( R_A^h \right ) \over R_A^h} = 
      \sqrt{ \left ( {\sum {\omega^h_A}^2 \over \left (\sum \omega^h_A \right )^2} \right ) 
           + \left ( {\sum {\omega^e_A}^2 \over \left (\sum \omega^e_A \right )^2} \right ) 
           + \left ( {\sum {\omega^h_D}^2 \over \left (\sum \omega^h_D \right )^2} \right ) 
           + \left ( {\sum {\omega^e_D}^2 \over \left (\sum \omega^e_D \right )^2} \right ) }
\end{equation}
 and 
\begin{equation}
\begin{split}
\left ( \delta \left ( \Delta \langle P_\perp^2 \rangle \right ) \right )^2 = 
   \left ({{\sum \omega^h_A P_\perp^4 }\over{\sum \omega^h_A}} - \left ({\sum \omega^h_A P_\perp^2 }\over{\sum \omega^h_A}\right )^2 \right ) 
         \times \left ( {\sum \left ( {\omega^h_A}^2 \right ) \over \left ( \sum \omega^h_A \right ) ^2 }\right ) \\
 + \left ({{\sum \omega^h_D P_\perp^4 }\over{\sum \omega^h_D}} - \left ({\sum \omega^h_D P_\perp^2 }\over{\sum \omega^h_D}\right )^2 \right ) 
	 \times \left ( {\sum \left ( {\omega^h_D}^2 \right ) \over \left ( \sum \omega^h_D \right ) ^2 }\right ).
\end{split}
\end{equation}

@@

To provide a first idea on data quality, we present in figure~\ref{fig:prelim} 
few preliminary results, before the application 
of any corrections. These preliminary results will also be used to 
illustrate the effects of the corrections discussed below.

@@

The acceptance correction consists of applying weights to the experimental data
events by events to correct for detection inefficiencies of the detectors.
Incidentally, it also corrects for small other issues of detection,
such as misidentification and scattering on detectors materials. The quality 
of the correction depends on the ability of the simulation to reproduce the 
experiment, the statistics accumulated and the size of interfering effects, such 
as bin migration. For this correction, we applied the method from the 
approved and published analysis from the same eg2 data~\cite{ElFassi:2008}.

@@

Then the simulated data are processed in a similar way than the experimental data by 
applying the cuts described in the section \ref{sec:pid}. Overall the 
simulation reproduces quite well the detectors responses, yet two issues might 
affect us and have to be understood. First, the efficiency of the CC is 
overestimated in the simulation. 
On the electron side the signal is a little stronger in the simulation (11 
photo-electrons) compared to experimental data (8 photo-electrons), but this 
feature should not affect us too much, because we are cutting only the tail of the 
distribution in both cases. 
Second, since the simulation has a perfect alignment of the beam with CLAS the 
vertex cuts do not need to be shifted from one sector to another. Therefore, 
we do not apply the shift from the table \ref{tab:vertex} to the simulation; 
the resulting cuts are shown in figure~\ref{simvertex}.

@@

The kinematic distributions from the simulation are compared to the 
experimental ones. This is important for the acceptance correction, to see 
whether or not, we can integrate over these variables in this correction.
Comparisons between simulated and experimental data are shown in figures 
\ref{fig:compNuQ2} to \ref{fig:compPhih}. The agreement is reasonable, but not 
perfect. The differences are due to the PYTHIA simulation, which is not including some 
physical effects, such as radiative and diffractive processes.

@@

The experimental data are corrected using weights defined as $\omega = 1/\text{Acc}$. The 
$\omega$ coefficient are calculated in many bins, in order to be independent of 
the imperfections of the event generator. However, an excess of bin could results into a strong 
bin migration\footnote{Fraction of events not reconstructed in the bin they 
were produced in.}, which might introduce a bias if it becomes a large effect.

We used a 4-dimensional binning to divide the large phase space available to 
our two particle final state. To evaluate the systematic error 
associated to this correction, we uses the two different binning
presented in table~\ref{tab:AcceptBinning}. The total number of bins is 
constrained by the amount of data generated and must be maintained 
reasonably low in order to keep a good statistical precision and manageable 
bin migration.

@@

The weights ($\omega_{\pi^\pm}(\nu,x_{Bj},p_h,t)$) are then extracted from 
the simulation using equation \ref{eq:acc}, however, it appears that these should not be used directly.
Three factors are sources of problematic bins:
\begin{itemize}
 \item too large weight values, i.e. very small acceptance;
 \item very few events reconstructed, leading to large statistical errors;
 \item large fraction of events originally generated in an other bin (bin migration).
\end{itemize}
To remove these bins we apply the following cuts:
\begin{equation} \label{eq:AccL1}
\left ({\delta \omega \over \omega}\right ) ^2 \times R_c \times \omega < 2,
\end{equation}
and
\begin{equation} \label{eq:AccL2}
N_{rec} > 4,
\end{equation}
$\delta \omega / \omega$ is the relative error on the weight and $R_c$ the 
proportion of reconstructed events initially generated in another bin. Figure 
\ref{fig:AccCoef} shows the distributions of $\omega$, after the cuts. Around 
900 bins remain for both targets, but we notice that weights are much larger 
for $\pi^-$, indicating a larger correction, compared to $\pi^+$. In order to 
maximize the acceptance and reduce the sensitivity to the cuts applied on the 
weights, which are arbitrary, the bin weights are corrected. We apply a 
reweighting by calculating a new acceptance in a two dimensional binning:
\begin{equation}
\text{Acc}_2(\nu,p_h) = {\sum_{rec} \omega (\nu,x_{Bj},p_h,t)\over N_{gen}(\nu,p_h)}.
\end{equation}
$\omega$ is the previously calculated weights or $1$ when the 
bin was excluded by the cuts.
One of the criteria for setting the limits in equation \ref{eq:AccL1} and 
\ref{eq:AccL2} is to keep reweighting factors $\omega_2 = 1/\text{Acc}_2$ at a few 
percents level.

@@

The electron acceptance, which is necessary in order to correct the number of electrons 
in the multiplicity ratios, is done following the same method as in the 
semi-inclusive case, but only using the two first dimensions ($\nu$ 
and $Q^2$). However, reweighting is not used 
for electrons as all non-empty bins pass the cuts \ref{eq:AccL1} and 
\ref{eq:AccL2}.

\begin{figure}[tbp]
\centering
\includegraphics[width=7.4cm] {chap5-fig/b_RvA.png} 
\includegraphics[width=7.4cm] {chap5-fig/b_RvZ.png} 
\includegraphics[width=7.4cm] {chap5-fig/b_PvA.png} 
\includegraphics[width=7.4cm] {chap5-fig/b_PvQ2.png} 
\caption {Preliminary results are compared with acceptance corrected ones, 
for multiplicity ratios (top) and transverse momentum broadening 
(bottom). Only statistical errors are shown.}
\label{fig:AcceptPlots}
\end{figure}

Figure \ref{fig:AcceptPlots}, where only statistical errors are 
represented, shows the new results after applying the acceptance correction.
The acceptance correction effects appear to be of the order of $10$\% for 
multiplicity ratios and 
$30$\% for transverse momentum broadening. This is a surprisingly 
significant correction in regard to the few centimeters between the two targets. 
The reason for such a large correction is that the small shift in $z$ position changes 
slightly the minimum angle of the detector in the region where most hadron production 
is concentrated, {\it i.e.} at low \pt close to the beam line. The 
$\pi^-$s appears to be more affected, which is due to the inbending magnetic 
field. Indeed, the low \pt $\pi^-$s have very low acceptance, leading to large 
correction factors. The large spread in weights makes the errors 
on \dpt very large and the related results difficult to exploit. 
Looking at the results themselves after the correction, we notice that now 
the transverse momentum broadening of both pions match, which is consistent 
with HERMES results.
